\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip} 	
\usepackage{tikz}

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}
\usepackage{enumitem}

\newcolumntype{C}{>{\centering\arraybackslash}X} 

\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyfoot[L]{\footnotesize Last updated: \today}
\fancyfoot[R]{\footnotesize{Latest version: \href{https://kyri04.github.io/cv}{kyri04.github.io/cv}}}
\fancyfoot[C]{}

\fancyhead[L]{}
\fancyhead[C]{}
\fancyhead[R]{\href{https://kyri04.github.io/cv}{Latest version \exlink}}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{20pt}

\usepackage{fontawesome5}

\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
  {%
    % End previous paragraph and insert a controlled vertical skip
    \par\addvspace{0\baselineskip}% <--- adjust to taste

    % Heading line
    \noindent
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
      \textbf{#1} & \hfill & #2 \\
    \end{tabularx}

    % Bullet list with fully controlled spacing (no stretch)
    \begin{minipage}[t]{\linewidth}
      \setlength{\parskip}{0pt}% ignore global parskip inside
      \begin{itemize}[
        leftmargin=1em,
        label=--,
        itemsep=3pt,
        topsep=4pt,
        parsep=0pt,
        partopsep=0pt
      ]
  }
  {%
      \end{itemize}
    \end{minipage}%
  }


\newcommand{\exlink}{%
\tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
    \begin{scope}[x=1ex, y=1ex]
        \clip (-0.1,-0.1) 
            --++ (-0, 1.2) 
            --++ (0.6, 0) 
            --++ (0, -0.6) 
            --++ (0.6, 0) 
            --++ (0, -1);
        \path[draw, 
            line width = 0.5, 
            rounded corners=0.5] 
            (0,0) rectangle (1,1);
    \end{scope}
    \path[draw, line width = 0.5] (0.5, 0.5) 
        -- (1, 1);
    \path[draw, line width = 0.5] (0.6, 1) 
        -- (1, 1) -- (1, 0.6);
    }
}


%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
% \pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Kyriacos Kyriacou} \\[7.5pt]
\small{Research Assistant in Early Detection Cancer Research at Keele University} \\
\href{https://github.com/kyri04}{\raisebox{-0.05\height}\faGithub\ kyri04} \ $|$ \ 
\href{https://linkedin.com/in/kyriacos-kyriacou-ba20622b8}{\raisebox{-0.05\height}\faLinkedin\ kyriacos-kyriacou-ba20622b8} \ $|$ \ 
% \href{https://mysite.com}{\raisebox{-0.05\height}\faGlobe \ mysite.com} \ $|$ \ 
\href{mailto:k.kyriacou@keele.ac.uk}{\raisebox{-0.05\height}\faEnvelope \ k.kyriacou@keele.ac.uk} \ $|$ \ 
\href{tel:+44 7401055190}{\raisebox{-0.05\height}\faMobile \ +44 7401055190} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
% \section{Keywords}
% \begin{center}
%     Machine Learning $\cdot$ Bioinformatics $\cdot$ Physics
% \end{center}

%Experience
% \section{Experience}

% % \begin{jobshort}{Research Associate at Keele University}{Oct 2025 - present}
% % A range of research projects developing machine learning models for early cancer detection.
% % \end{jobshort}

% \begin{joblong}{Research Associate at Keele University}{Oct 2025 - present}
% \item A range of research projects developing machine learning models for early cancer detection.
% \item Drafting a paper on predicting prostate cancer diagnosis and ISUP grade using machine learning and X-ray scattering.
% \end{joblong}

% \begin{joblong}{Summer Intern at Keele University}{Jun 2025 - Aug 2024}
% \item Developed models to identify cancer in X-ray scattering of biopsied
% prostate and breast tissue samples.
% \item Conducted research on I22 at the Diamond Light Source.
% \item Presented my work for an Institute of Physics talk, a CRUK funded Tissue Microenvironment and Disease workshop, patient advocate sessions and various
% departmental seminars.
% \end{joblong}

%Projects
\section{Recent Projects and Experience}
\begin{joblong}{Early Cancer Detection using Machine Learning and X-ray Scattering}{}
\item Developed models to reliably detect cancer in X-ray scattering of biopsied tissue samples.
\item Identified key structural biomarkers for prostate and breast cancer.
\item Conducted research on I22 at the {Diamond Light Source}.
\item Drafting a manuscript on machine learning prediction of prostate cancer diagnosis and ISUP grade.
\item Delivered talks for an Institute of Physics seminar and a CRUK funded Disease Workshop.
\end{joblong}

\begin{joblong}{Developer of \texttt{signalearn}}{\href{https://github.com/kyri04/signalearn}{github.com/kyri04/signalearn}}
\item Developed a python library to abstract machine learning workflows with series datasets.
% \item Working towards a graphical interface that enables use of the library without programming knowledge.
\end{joblong}

\begin{joblong}{Measurement of Taste Attributes in Fruit using Machine Learning}{Third Year Project}
\item Developed models to measure crispiness, soureness and sweetness from ultrasonic measurements of fruit.
\item Improves standard industrial processes which are slow, destructive, expensive and subjective.
\end{joblong}

\begin{joblong}{Exoplanet Habitability Prediction with Machine Learning}{Module Project}
% \item Synthesised thousands of expolanet transmission spectra with a diverse range of atmospheric compositions, cloud/haze treatments and surface temperatures.
% \item Synthesised thousands of exoplanet transmission spectra to compensate for the lack of real data, with a diverse range of atmospheric conditions, cloud/haze treatments, and surface temperatures.
% \item Trained models on the simulated spectra that accurately predict the habitability index of real spectra.
% \item Trained on simulated exoplanet spectra to address limited real data and predict the habitability of real observations.
% \item Synthesised and trained models on thousands of exoplanet transmission spectra with a diverse range of atmospheric conditions, cloud/haze treatments, and surface temperatures to predict 
% the habitability index of real exoplanets.
\item Synthesised and trained models on diverse transmission spectra to predict habitability of real exoplanets.
\end{joblong}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}} 2022 - 2025 & Physics BSc at
\textbf{Keele University} \hfill (2:1) \\ 
2020 - 2022 & A-levels at \textbf{St John Fisher Catholic College Trinity Sixth
Form} \hfill (A$^*$ABBC) \\ 
\end{tabularx}

\section{Awards and Scholarships}
\begin{jobshort}{Tissue Microenvironment and Disease Workshop Presentation Prize Winner}{July 2025}
Awarded £100 second prize for oral presentation at a Tissue Microenvironment and
Disease workshop at Keele Hall, funded by Cancer Research UK.
\end{jobshort}

\begin{jobshort}{Bob Gould Prize Winner \href{https://www.keele.ac.uk/students/academicandlearningsupport/awardsandprizes/undergraduateawardsandprizes/chemicalandphysicalsciences/}{\exlink}}{July 2025}
Awarded the Bob Gould Prize for most outstanding performance in the third year
Physics project.
\end{jobshort}

\begin{jobshort}{Summer Research Bursary Winner}{May 2024}
Awarded a competitive £1600 summer research bursary following my proposal to
explore machine learning analysis of X-ray scattering for early cancer detection
at Keele University.
\end{jobshort}

\begin{jobshort}{FLOURISH Bursary Winner \href{https://www.keele.ac.uk/business/researchdevelopmentandinnovation/flourish/}{\exlink}}{August 2024}
Awarded a competitive £1200 bursary to assist in digital marketing strategies with Exesios BDD.
\end{jobshort}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
% \section{Publications}
% \begin{refsection}[citations.bib]
% \nocite{*}
% \printbibliography[heading=none]
% \end{refsection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills, Hobbies and Interests}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Karate} &  \small{1st Dan Black Belt \& Instructor $\cdot$ Club Captain in 2024 $\cdot$ Social Media Officer in 2025.}\\
\textbf{Piano} &  \small{Distinction in Grade 8 $\cdot$ Teaching piano part-time $\cdot$ \href{https://www.instagram.com/kyriskeys}{@kyriskeys}.}\\
\textbf{Photography} &  \small{Photographing for City Bloc, NUBS, Keele Football, Stoke-on-Clay \& more $\cdot$ \href{https://www.instagram.com/kyrisphotos}{@kyrisphotos}.}\\
\textbf{Game Dev.} &  \small{Developer of \href{https://store.steampowered.com/app/2648310/Rocket_Smash/}{Rocket Smash}, experience with Unity and Unreal Engine.}\\
\textbf{Technical} &  \small{Experience with Python, C\#, \LaTeX, JavaScript, HTML, CSS, PHP, Rust.}\\
\end{tabularx}

% \vfill
% \center{\footnotesize Last updated: \today}

\end{document}
